### 2017-10-14 paper/sexSelectionSpacingAppendix-ver1.tex
Rename all graphs and update Makefile with dependencies/targets
Instead of a numbering system, which was hard to read, all graphs
are now named with urban/rural and the sex composition of prior
children, if any.

All references in paper and appendix changed to fit the new
naming system.

The Makefile was update as well and now include the relevant
targets and dependencies with the new naming system. In principle,
it should be possible to shorten the generation of the dependencies
and targets, but that would require an if statement and the if
function in Make runs of whether a given piece of te

% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}

@@

% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}

@@

% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}

@@

% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}

@@

% \begin{figure}[htpb!]
% \subfloat[1972--1984 (N=4,518)]{
% \begin{minipage}{0.28\textwidth}
% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_pc}}\\
% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_s}} 
% \subfloat[1985--1994 (N=4,309)]{
% \begin{minipage}{0.28\textwidth}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_s}}
% \begin{minipage}{0.28\textwidth}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_s}}
% \subfloat[1972--1984 (N=25,486)]{
% \begin{minipage}{0.28\textwidth}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_s}} 
% \subfloat[1985--1994 (N=23,360)]{
% \begin{minipage}{0.28\textwidth}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_s}}
% \begin{minipage}{0.28\textwidth}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_s}}
% \label{fig:results_spell1_low}
% \subfloat[1972--1984 (N=3,666)]{
% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_pc}}\\
% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_s}} 
% \subfloat[1985--1994 (N=4,104)]{
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_s}}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_s}}
% \subfloat[1972--1984 (N=7,496)]{
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_s}} 
% \subfloat[1985--1994 (N=9,000)]{
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_s}}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_s}}
% \label{fig:results_spell1_med}
% \subfloat[1972--1984 (N=7,338)]{
% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_pc}}\\
% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_s}} 
% \subfloat[1985--1994 (N=11,045)]{
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_s}}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_s}}
% \subfloat[1972--1984 (N=3,933)]{
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_s}} 
% \subfloat[1985--1994 (N=8,027)]{
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_s}}
% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_s}}
% \label{fig:results_spell1_high}

@@

% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_pc}}\\
% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_s}} 

@@

% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_s}}

@@

% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_s}}

@@

% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_s}} 

>>>>

% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}

@@

% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_s}}

@@

% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_s}}

@@

% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_s}} 

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_s}}

@@

% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_s}}

@@

\begin{figure}[htpb!]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=4,518)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,309)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,762)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=25,486)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=23,360)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,922)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with no education by quarter (3 month
period). 
Predictions based on age 16 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_low}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=3,666)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,104)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,302)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=7,496)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=9,000)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=5,208)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
period). 
Predictions based on age 17 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_med}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=7,338)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=11,045)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=9,116)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=3,933)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=8,027)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,504)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 8 or more years of education by quarter
(3 month period). 
Predictions based on age 20 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_high}
\end{figure}

@@

% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_urban_pc}}\\
% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_urban_s}} 

@@

% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_urban_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_urban_s}}

@@

% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_urban_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_urban_s}}

@@

% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_rural_pc}}\\
% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_rural_s}} 
